### 2023-02-16 notebooks/conformal.qmd
woohoo

```{julia}
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
```

>>>>

```{julia}
#| output: true
#| echo: false

ordered_names = [
    "Generic (γ=0.5)",
    "Generic (γ=0.9)",
    "Conformal (λ₂=1)",
    "Conformal (λ₂=10)"
]

# Generators:
generators = Dict(
    ordered_names[1] => GenericGenerator(opt = opt, decision_threshold=0.5),
    ordered_names[2] => GenericGenerator(opt = opt, decision_threshold=0.9),
    ordered_names[3] => CCE.ConformalGenerator(opt=opt, λ=[0.1,1]),
    ordered_names[4] => CCE.ConformalGenerator(opt=opt, λ=[0.1,10]),
)

counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen; initialization=:identity) for (name, gen) in generators])

# Plots:
plts = []
for name ∈ ordered_names
    ce = counterfactuals[name]
    plt = plot(ce; title=name, colorbar=false, ticks = false, legend=false, zoom=0)
    plts = vcat(plts..., plt)
end
_n = length(generators)
img_size = 300
plot(plts..., size=(_n * img_size,1.05*img_size), layout=(1,_n))
```
